Simulating Financial Markets using MASON Framework\thanks{Prepared for the 2nd World Congress on Social Simulation, GMU, Fairfax, 14--17 July, 2008.}

### 2008-05-08 documents/WCSS2008Paper/paper.tex
Added Hurst exponent exploration for Cont to the paper.

\begin{figure}[htbp]
  \begin{center}
   \mbox{
      \subfigure[Autocorrelation functions]{\scalebox{0.45}{\quad \quad \includegraphics[width=1.0\textwidth]{../graphics/comparisonOfACFs.pdf}}} \quad
      \subfigure[Return distributions]{\scalebox{0.45}{\includegraphics[width=1.00\textwidth]{../graphics/comparisonOfHistograms.pdf}}}
      }
    \caption{Autocorrelation and distributions in Cont simulation with $s=0.1$ and varying $D$, averaged over many runs.}
    \label{fig:ContMultiRun}
  \end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
  \begin{center}
   \mbox{
      \subfigure[Autocorrelation functions]{\scalebox{0.45}{\quad \quad \includegraphics[width=1.0\textwidth]{../graphics/comparisonOfACFs.pdf}}} \quad
      \subfigure[Return distributions]{\scalebox{0.45}{\includegraphics[width=1.00\textwidth]{../graphics/comparisonOfHistograms.pdf}}}
      }

      \subfigure[Hurst exponents for different $s$]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth, angle=270]{../graphics/comparisonOfHurstsS}}} 
      \subfigure[Hurst exponents for different $D$]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth, angle=270]{../graphics/comparisonOfHurstsD}}}

    \caption{Autocorrelation and distributions in Cont simulation with $s=0.1$ and varying $D$, averaged over many runs. In bottom row, kernel regresion on Hurst exponents of time series generated from Con't model for varying levels of $s$ and $D$ is presented.}
    \label{fig:ContMultiRun}
  \end{center}
\end{figure}
